### 2025-07-19 evaluating-prediction-accuracy.qmd
20250719 - summarizing accuracy by position

The association between projected and actual fantasy points tended to flatten at the higher levels of projected points, for some positions, including Running Backs, Kickers, and defensive players.
A consequence of this pattern, from the perspective of draft strategy, is that it would not make sense to draft players projected to score more than the flattening of the projected–actual curve.
For instance, drafting a highly routed Wide Receiver may be safer than drafting a highly ranked Running Back, who may be more prone to injury.
This finding was echoed by @Kartes2025 (archived at <https://perma.cc/R3WS-CAKD>) whose evaluation of the accuracy of projections by position found that:

@@

We calculate the 95% prediction interval based on a LOESS model, which allows nonlinear associations, using the `loess.sd()` function of the `msir` package [@R-msir; @Scrucca2011_packages].

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

The association between projected and actual fantasy points tended to flatten at the higher levels of projected points, for some positions, including Running Backs, Kickers, and defensive players.
A consequence of this pattern, from the perspective of draft strategy, is that it would not make sense to draft players projected to score more than the flattening of the projected–actual curve.
For instance, drafting a highly routed Wide Receiver may be safer than drafting a highly ranked Running Back, who may be more prone to injury.
This finding is consistent with findings from @Petersen2017 [archived at <https://perma.cc/BG2W-ANUF>], who found that projections were more accurate for Quarterbacks and Wide Receivers than for Running Backs; projections were the least accurate for Kickers, Defensive Backs, and Defense/Special Teams.
These finding were also extended by @Kartes2025 (archived at <https://perma.cc/R3WS-CAKD>) whose evaluation of the accuracy of projections by position found that:

@@

accuracyIndices_seasonal_overall <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal$raw_points,
  actual = projectionsWithActuals_seasonal$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_overall <- round(accuracyIndices_seasonal_overall$rsquared, digits = 2)
me_seasonal_overall <- round(accuracyIndices_seasonal_overall$ME, digits = 2)
mae_seasonal_overall <- round(accuracyIndices_seasonal_overall$MAE, digits = 2)
```

A calibration plot of the seasonal projections for all players (across all positions) is in @fig-calibrationPlotSeasonalOverall.
We calculate the 95% prediction interval based on a LOESS model, which allows nonlinear associations, using the `loess.sd()` function of the `msir` package [@R-msir; @Scrucca2011_packages].

@@

Here are the seasonal accuracy indexes for players across all positions, but only among those who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_seasonal_overall_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_overall_subset <- round(accuracyIndices_seasonal_overall_subset$rsquared, digits = 2)
me_seasonal_overall_subset <- round(accuracyIndices_seasonal_overall_subset$ME, digits = 2)
mae_seasonal_overall_subset <- round(accuracyIndices_seasonal_overall_subset$MAE, digits = 2)
```

@@

Here are the seasonal accuracy indexes for all Quarterbacks:

@@

accuracyIndices_seasonal_qb <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_qb$raw_points,
  actual = projectionsWithActuals_seasonal_qb$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_qb <- round(accuracyIndices_seasonal_qb$rsquared, digits = 2)
me_seasonal_qb <- round(accuracyIndices_seasonal_qb$ME, digits = 2)
mae_seasonal_qb <- round(accuracyIndices_seasonal_qb$MAE, digits = 2)
```

A calibration plot of the seasonal projections for Quarterbacks is in @fig-calibrationPlotSeasonalQBs.

@@

Here are the seasonal accuracy indexes for only those Quarterbacks who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_seasonal_qb_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_qb$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_qb$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_qb_subset <- round(accuracyIndices_seasonal_qb_subset$rsquared, digits = 2)
me_seasonal_qb_subset <- round(accuracyIndices_seasonal_qb_subset$ME, digits = 2)
mae_seasonal_qb_subset <- round(accuracyIndices_seasonal_qb_subset$MAE, digits = 2)
```

@@

Here are the seasonal accuracy indexes for all Running Backs:

@@

accuracyIndices_seasonal_rb <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_rb$raw_points,
  actual = projectionsWithActuals_seasonal_rb$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_rb <- round(accuracyIndices_seasonal_rb$rsquared, digits = 2)
me_seasonal_rb <- round(accuracyIndices_seasonal_rb$ME, digits = 2)
mae_seasonal_rb <- round(accuracyIndices_seasonal_rb$MAE, digits = 2)
```

A calibration plot of the seasonal projections for Running Backs is in @fig-calibrationPlotSeasonalRBs.

@@

Here are the seasonal accuracy indexes for only those Running Backs who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_seasonal_rb_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_rb$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_rb$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_rb_subset <- round(accuracyIndices_seasonal_rb_subset$rsquared, digits = 2)
me_seasonal_rb_subset <- round(accuracyIndices_seasonal_rb_subset$ME, digits = 2)
mae_seasonal_rb_subset <- round(accuracyIndices_seasonal_rb_subset$MAE, digits = 2)
```

@@

accuracyIndices_seasonal_wr <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_wr$raw_points,
  actual = projectionsWithActuals_seasonal_wr$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_wr <- round(accuracyIndices_seasonal_wr$rsquared, digits = 2)
me_seasonal_wr <- round(accuracyIndices_seasonal_wr$ME, digits = 2)
mae_seasonal_wr <- round(accuracyIndices_seasonal_wr$MAE, digits = 2)
```

A calibration plot of the seasonal projections for Wide Receivers is in @fig-calibrationPlotSeasonalWRs.

@@

Here are the seasonal accuracy indexes for only those Wide Receivers who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_seasonal_wr_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_wr$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_wr$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_wr_subset <- round(accuracyIndices_seasonal_wr_subset$rsquared, digits = 2)
me_seasonal_wr_subset <- round(accuracyIndices_seasonal_wr_subset$ME, digits = 2)
mae_seasonal_wr_subset <- round(accuracyIndices_seasonal_wr_subset$MAE, digits = 2)
```

@@

accuracyIndices_seasonal_te <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_te$raw_points,
  actual = projectionsWithActuals_seasonal_te$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_te <- round(accuracyIndices_seasonal_te$rsquared, digits = 2)
me_seasonal_te <- round(accuracyIndices_seasonal_te$ME, digits = 2)
mae_seasonal_te <- round(accuracyIndices_seasonal_te$MAE, digits = 2)
```

A calibration plot of the seasonal projections for Tight Ends is in @fig-calibrationPlotSeasonalTEs.

@@

Here are the seasonal accuracy indexes for only those Tight Ends who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_seasonal_te_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_te$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_te$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_te_subset <- round(accuracyIndices_seasonal_te_subset$rsquared, digits = 2)
me_seasonal_te_subset <- round(accuracyIndices_seasonal_te_subset$ME, digits = 2)
mae_seasonal_te_subset <- round(accuracyIndices_seasonal_te_subset$MAE, digits = 2)
```

@@

accuracyIndices_seasonal_k <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_k$raw_points,
  actual = projectionsWithActuals_seasonal_k$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_k <- round(accuracyIndices_seasonal_k$rsquared, digits = 2)
me_seasonal_k <- round(accuracyIndices_seasonal_k$ME, digits = 2)
mae_seasonal_k <- round(accuracyIndices_seasonal_k$MAE, digits = 2)
```

A calibration plot of the seasonal projections for Kickers is in @fig-calibrationPlotSeasonalKs.

@@

Here are the seasonal accuracy indexes for only those Kickers who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_seasonal_k_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_k$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_k$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_k_subset <- round(accuracyIndices_seasonal_k_subset$rsquared, digits = 2)
me_seasonal_k_subset <- round(accuracyIndices_seasonal_k_subset$ME, digits = 2)
mae_seasonal_k_subset <- round(accuracyIndices_seasonal_k_subset$MAE, digits = 2)
```

@@

accuracyIndices_seasonal_dl <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_dl$raw_points,
  actual = projectionsWithActuals_seasonal_dl$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_dl <- round(accuracyIndices_seasonal_dl$rsquared, digits = 2)
me_seasonal_dl <- round(accuracyIndices_seasonal_dl$ME, digits = 2)
mae_seasonal_dl <- round(accuracyIndices_seasonal_dl$MAE, digits = 2)
```

A calibration plot of the seasonal projections for Defensive Linemen is in @fig-calibrationPlotSeasonalDLs.

@@

Here are the seasonal accuracy indexes for only those Defensive Linemen who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_seasonal_dl_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_dl$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_dl$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_dl_subset <- round(accuracyIndices_seasonal_dl_subset$rsquared, digits = 2)
me_seasonal_dl_subset <- round(accuracyIndices_seasonal_dl_subset$ME, digits = 2)
mae_seasonal_dl_subset <- round(accuracyIndices_seasonal_dl_subset$MAE, digits = 2)
```

@@

accuracyIndices_seasonal_lb <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_lb$raw_points,
  actual = projectionsWithActuals_seasonal_lb$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_lb <- round(accuracyIndices_seasonal_lb$rsquared, digits = 2)
me_seasonal_lb <- round(accuracyIndices_seasonal_lb$ME, digits = 2)
mae_seasonal_lb <- round(accuracyIndices_seasonal_lb$MAE, digits = 2)
```

A calibration plot of the seasonal projections for Linebackers is in @fig-calibrationPlotSeasonalLBs.

@@

Here are the seasonal accuracy indexes for only those Linebackers who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_seasonal_lb_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_lb$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_lb$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_lb_subset <- round(accuracyIndices_seasonal_lb_subset$rsquared, digits = 2)
me_seasonal_lb_subset <- round(accuracyIndices_seasonal_lb_subset$ME, digits = 2)
mae_seasonal_lb_subset <- round(accuracyIndices_seasonal_lb_subset$MAE, digits = 2)
```

@@

accuracyIndices_seasonal_db <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_db$raw_points,
  actual = projectionsWithActuals_seasonal_db$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_seasonal_db <- round(accuracyIndices_seasonal_db$rsquared, digits = 2)
me_seasonal_db <- round(accuracyIndices_seasonal_db$ME, digits = 2)
mae_seasonal_db <- round(accuracyIndices_seasonal_db$MAE, digits = 2)
```

A calibration plot of the seasonal projections for Defensive backs is in @fig-calibrationPlotSeasonalDBs.

@@

Here are the seasonal accuracy indexes for only those Defensive Backs who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_seasonal_db_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_db$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_db$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)

rsquare_seasonal_db_subset <- round(accuracyIndices_seasonal_db_subset$rsquared, digits = 2)
me_seasonal_db_subset <- round(accuracyIndices_seasonal_db_subset$ME, digits = 2)
mae_seasonal_db_subset <- round(accuracyIndices_seasonal_db_subset$MAE, digits = 2)
```

@@

accuracyIndices_weekly_overall <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly$raw_points,
  actual = projectionsWithActuals_weekly$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_overall <- round(accuracyIndices_weekly_overall$rsquared, digits = 2)
me_weekly_overall <- round(accuracyIndices_weekly_overall$ME, digits = 2)
mae_weekly_overall <- round(accuracyIndices_weekly_overall$MAE, digits = 2)
```

A calibration plot of the weekly projections for all players (across all positions) is in @fig-calibrationPlotWeeklyOverall.

@@

Here are the weekly accuracy indexes for players across all positions, but only among those who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_weekly_overall_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)

rsquare_weekly_overall_subset <- round(accuracyIndices_weekly_overall_subset$rsquared, digits = 2)
me_weekly_overall_subset <- round(accuracyIndices_weekly_overall_subset$ME, digits = 2)
mae_weekly_overall_subset <- round(accuracyIndices_weekly_overall_subset$MAE, digits = 2)
```

@@

accuracyIndices_weekly_qb <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_qb$raw_points,
  actual = projectionsWithActuals_weekly_qb$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_qb <- round(accuracyIndices_weekly_qb$rsquared, digits = 2)
me_weekly_qb <- round(accuracyIndices_weekly_qb$ME, digits = 2)
mae_weekly_qb <- round(accuracyIndices_weekly_qb$MAE, digits = 2)
```

A calibration plot of the weekly projections for Quarterbacks is in @fig-calibrationPlotWeeklyQBs.

@@

Here are the weekly accuracy indexes for only those Quarterbacks who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_weekly_qb_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_qb$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_qb$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)

rsquare_weekly_qb_subset <- round(accuracyIndices_weekly_qb_subset$rsquared, digits = 2)
me_weekly_qb_subset <- round(accuracyIndices_weekly_qb_subset$ME, digits = 2)
mae_weekly_qb_subset <- round(accuracyIndices_weekly_qb_subset$MAE, digits = 2)
```

@@

accuracyIndices_weekly_rb <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_rb$raw_points,
  actual = projectionsWithActuals_weekly_rb$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_rb <- round(accuracyIndices_weekly_rb$rsquared, digits = 2)
me_weekly_rb <- round(accuracyIndices_weekly_rb$ME, digits = 2)
mae_weekly_rb <- round(accuracyIndices_weekly_rb$MAE, digits = 2)
```

A calibration plot of the weekly projections for Running Backs is in @fig-calibrationPlotWeeklyRBs.

@@

Here are the weekly accuracy indexes for only those Running Backs who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_weekly_rb_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_rb$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_rb$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)

rsquare_weekly_rb_subset <- round(accuracyIndices_weekly_rb_subset$rsquared, digits = 2)
me_weekly_rb_subset <- round(accuracyIndices_weekly_rb_subset$ME, digits = 2)
mae_weekly_rb_subset <- round(accuracyIndices_weekly_rb_subset$MAE, digits = 2)
```

@@

accuracyIndices_weekly_wr <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_wr$raw_points,
  actual = projectionsWithActuals_weekly_wr$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_wr <- round(accuracyIndices_weekly_wr$rsquared, digits = 2)
me_weekly_wr <- round(accuracyIndices_weekly_wr$ME, digits = 2)
mae_weekly_wr <- round(accuracyIndices_weekly_wr$MAE, digits = 2)
```

A calibration plot of the weekly projections for Wide Receivers is in @fig-calibrationPlotWeeklyWRs.

@@

Here are the weekly accuracy indexes for only those Wide Receivers who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_weekly_wr_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_wr$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_wr$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)

rsquare_weekly_wr_subset <- round(accuracyIndices_weekly_wr_subset$rsquared, digits = 2)
me_weekly_wr_subset <- round(accuracyIndices_weekly_wr_subset$ME, digits = 2)
mae_weekly_wr_subset <- round(accuracyIndices_weekly_wr_subset$MAE, digits = 2)
```

@@

accuracyIndices_weekly_te <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_te$raw_points,
  actual = projectionsWithActuals_weekly_te$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_te <- round(accuracyIndices_weekly_te$rsquared, digits = 2)
me_weekly_te <- round(accuracyIndices_weekly_te$ME, digits = 2)
mae_weekly_te <- round(accuracyIndices_weekly_te$MAE, digits = 2)
```

A calibration plot of the weekly projections for Tight Ends is in @fig-calibrationPlotWeeklyTEs.

@@

Here are the weekly accuracy indexes for only those Tight Ends who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_weekly_te_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_te$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_te$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)

rsquare_weekly_te_subset <- round(accuracyIndices_weekly_te_subset$rsquared, digits = 2)
me_weekly_te_subset <- round(accuracyIndices_weekly_te_subset$ME, digits = 2)
mae_weekly_te_subset <- round(accuracyIndices_weekly_te_subset$MAE, digits = 2)
```

@@

accuracyIndices_weekly_k <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_k$raw_points,
  actual = projectionsWithActuals_weekly_k$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_k <- round(accuracyIndices_weekly_k$rsquared, digits = 2)
me_weekly_k <- round(accuracyIndices_weekly_k$ME, digits = 2)
mae_weekly_k <- round(accuracyIndices_weekly_k$MAE, digits = 2)
```

A calibration plot of the weekly projections for Kickers is in @fig-calibrationPlotWeeklyKs.

@@

Here are the weekly accuracy indexes for only those Kickers who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_weekly_k_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_k$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_k$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)

rsquare_weekly_k_subset <- round(accuracyIndices_weekly_k_subset$rsquared, digits = 2)
me_weekly_k_subset <- round(accuracyIndices_weekly_k_subset$ME, digits = 2)
mae_weekly_k_subset <- round(accuracyIndices_weekly_k_subset$MAE, digits = 2)
```

@@

accuracyIndices_weekly_dl <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_dl$raw_points,
  actual = projectionsWithActuals_weekly_dl$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_dl <- round(accuracyIndices_weekly_dl$rsquared, digits = 2)
me_weekly_dl <- round(accuracyIndices_weekly_dl$ME, digits = 2)
mae_weekly_dl <- round(accuracyIndices_weekly_dl$MAE, digits = 2)
```

A calibration plot of the weekly projections for Defensive Linemen is in @fig-calibrationPlotWeeklyDLs.

@@

Here are the weekly accuracy indexes for only those Defensive Linemen who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_weekly_dl_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_dl$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_dl$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)

rsquare_weekly_dl_subset <- round(accuracyIndices_weekly_dl_subset$rsquared, digits = 2)
me_weekly_dl_subset <- round(accuracyIndices_weekly_dl_subset$ME, digits = 2)
mae_weekly_dl_subset <- round(accuracyIndices_weekly_dl_subset$MAE, digits = 2)
```

@@

accuracyIndices_weekly_lb <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_lb$raw_points,
  actual = projectionsWithActuals_weekly_lb$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_lb <- round(accuracyIndices_weekly_lb$rsquared, digits = 2)
me_weekly_lb <- round(accuracyIndices_weekly_lb$ME, digits = 2)
mae_weekly_lb <- round(accuracyIndices_weekly_lb$MAE, digits = 2)
```

A calibration plot of the weekly projections for Linebackers is in @fig-calibrationPlotWeeklyLBs.

@@

Here are the weekly accuracy indexes for only those Linebackers who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_weekly_lb_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_lb$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_lb$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)

rsquare_weekly_lb_subset <- round(accuracyIndices_weekly_lb_subset$rsquared, digits = 2)
me_weekly_lb_subset <- round(accuracyIndices_weekly_lb_subset$ME, digits = 2)
mae_weekly_lb_subset <- round(accuracyIndices_weekly_lb_subset$MAE, digits = 2)
```

@@

accuracyIndices_weekly_db <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_db$raw_points,
  actual = projectionsWithActuals_weekly_db$fantasyPoints,
  dropUndefined = TRUE
)

rsquare_weekly_db <- round(accuracyIndices_weekly_db$rsquared, digits = 2)
me_weekly_db <- round(accuracyIndices_weekly_db$ME, digits = 2)
mae_weekly_db <- round(accuracyIndices_weekly_db$MAE, digits = 2)
```

A calibration plot of the weekly projections for Linebackers is in @fig-calibrationPlotWeeklyDBs.

@@

Here are the weekly accuracy indexes for only those Defensive Backs who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

accuracyIndices_weekly_db_subset <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_db$raw_points[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  actual = projectionsWithActuals_weekly_db$fantasyPoints[which(projectionsWithActuals_weekly$player_id_season_week %in% playersWithHighProjectedOrActualPoints_weekly)],
  dropUndefined = TRUE
)

rsquare_weekly_db_subset <- round(accuracyIndices_weekly_db_subset$rsquared, digits = 2)
me_weekly_db_subset <- round(accuracyIndices_weekly_db_subset$ME, digits = 2)
mae_weekly_db_subset <- round(accuracyIndices_weekly_db_subset$MAE, digits = 2)
```

### Summarizing the Accuracy By Position {#sec-predictionAccuracyByPosition}

seasonalAccuracy <- data.frame(
  position = c(
    "All",
    "Quarterbacks",
    "Running Backs",
    "Wide Receivers",
    "Tight Ends",
    "Kickers",
    "Defensive Linemen",
    "Linebackers",
    "Defensive Backs"
  ), 
  rsquared = c(
    rsquare_seasonal_overall,
    rsquare_seasonal_qb,
    rsquare_seasonal_rb,
    rsquare_seasonal_wr,
    rsquare_seasonal_te,
    rsquare_seasonal_k,
    rsquare_seasonal_dl,
    rsquare_seasonal_lb,
    rsquare_seasonal_db
  ),
  me = c(
    me_seasonal_overall,
    me_seasonal_qb,
    me_seasonal_rb,
    me_seasonal_wr,
    me_seasonal_te,
    me_seasonal_k,
    me_seasonal_dl,
    me_seasonal_lb,
    me_seasonal_db
  ),
  mae = c(
    mae_seasonal_overall,
    mae_seasonal_qb,
    mae_seasonal_rb,
    mae_seasonal_wr,
    mae_seasonal_te,
    mae_seasonal_k,
    mae_seasonal_dl,
    mae_seasonal_lb,
    mae_seasonal_db
  )
)

seasonalAccuracy_subset <- data.frame(
  position = c(
    "All",
    "Quarterbacks",
    "Running Backs",
    "Wide Receivers",
    "Tight Ends",
    "Kickers",
    "Defensive Linemen",
    "Linebackers",
    "Defensive Backs"
  ), 
  rsquared = c(
    rsquare_seasonal_overall_subset,
    rsquare_seasonal_qb_subset,
    rsquare_seasonal_rb_subset,
    rsquare_seasonal_wr_subset,
    rsquare_seasonal_te_subset,
    rsquare_seasonal_k_subset,
    rsquare_seasonal_dl_subset,
    rsquare_seasonal_lb_subset,
    rsquare_seasonal_db_subset
  ),
  me = c(
    me_seasonal_overall_subset,
    me_seasonal_qb_subset,
    me_seasonal_rb_subset,
    me_seasonal_wr_subset,
    me_seasonal_te_subset,
    me_seasonal_k_subset,
    me_seasonal_dl_subset,
    me_seasonal_lb_subset,
    me_seasonal_db_subset
  ),
  mae = c(
    mae_seasonal_overall_subset,
    mae_seasonal_qb_subset,
    mae_seasonal_rb_subset,
    mae_seasonal_wr_subset,
    mae_seasonal_te_subset,
    mae_seasonal_k_subset,
    mae_seasonal_dl_subset,
    mae_seasonal_lb_subset,
    mae_seasonal_db_subset
  )
)

weeklyAccuracy <- data.frame(
  position = c(
    "All",
    "Quarterbacks",
    "Running Backs",
    "Wide Receivers",
    "Tight Ends",
    "Kickers",
    "Defensive Linemen",
    "Linebackers",
    "Defensive Backs"
  ), 
  rsquared = c(
    rsquare_weekly_overall,
    rsquare_weekly_qb,
    rsquare_weekly_rb,
    rsquare_weekly_wr,
    rsquare_weekly_te,
    rsquare_weekly_k,
    rsquare_weekly_dl,
    rsquare_weekly_lb,
    rsquare_weekly_db
  ),
  me = c(
    me_weekly_overall,
    me_weekly_qb,
    me_weekly_rb,
    me_weekly_wr,
    me_weekly_te,
    me_weekly_k,
    me_weekly_dl,
    me_weekly_lb,
    me_weekly_db
  ),
  mae = c(
    mae_weekly_overall,
    mae_weekly_qb,
    mae_weekly_rb,
    mae_weekly_wr,
    mae_weekly_te,
    mae_weekly_k,
    mae_weekly_dl,
    mae_weekly_lb,
    mae_weekly_db
  )
)
